Occurrence and transmission potential of asymptomatic and pre-symptomatic SARS-CoV-2 infections: a living systematic review and meta-analysis

### 2021-10-18 Manuscript_draft.Rmd
Table Q2.2 updated

#subset df
Q2_2_table <- Q2_2_table %>%
  select(study, q3_setting)

q2_2_nstudies <- nrow(Q2_2_table) #total number of studies included in q1

>>>>

#subset df
Q2_2_table <- Q2_2_table %>%
  select(study, q3_setting)
Q2_2_table$q3_setting <- gsub(";([[:alpha:]])", "; \\1", Q2_2_table$q3_setting)
Q2_2_table$q3_setting <- gsub("/([[:alpha:]])", ", \\1", Q2_2_table$q3_setting)
q2_2_nstudies <- nrow(Q2_2_table) #total number of studies included in q1
